\LARGE \bf Approximately Orchestrated Road Traffic Automata:\\ Large-scale Traffic Simulation for Autonomous Vehicles

### 2012-03-15 papers/itsc_2012/final.tex
checking in edits to sections I through III based on Chiu's and Piyush's comments - also added acknowledgements blurb

Computational processing power has made excellent advancements in the last two
decades. Parallel computing has proved significant for traffic simulation
through the use of Geographic Information System (GIS) software
\cite{pursula1999simulation}. \commentpk{preceding sentence doesnt paraphrase
the ref correctly. double check}. Advanced computing techniques have enabled
microscopic models of traffic simulation to generate results at a meaningful
scale (city-wide or greater). As a result, a number of good micro-simulators
have been introduced in the past decade. We review a number of such simulators
in this section along with other relevant work.

A number of traffic simulators already make use of OSM data. MATSim is one such
multiagent simulator that focuses on performing large-scale simulations in a
relatively small amount of time \cite{balmer2009matsim}. Traffic demand is
supplied to MATSim in the form of \textit{plans} that an individual may intend
to follow in a given day. MATSim aims to iteratively improve these plans though
offline computation to maximize traffic throughput. In other words, it helps
individuals understand the best way to go about their daily routine to minimize
time spent in transit. This goal is somewhat different from that of AORTA,
where the demand supplied by individuals is taken as is. Rather than simply
improving routes, AORTA allows creating entirely different behaviors for both
vehicles and intersections.

Another popular open source traffic simulator that can use OSM data is SUMO
\cite{SUMO2011}, which shares the same goals as AORTA and is fairly similar at
a high level. SUMO has been used to study the effect of automated
transportation systems, route planning of individual vehicles, as well as
dynamically adapting traffic signal policies to increase traffic efficiency.
AORTA and SUMO differ in the manner in which intersections are handled. SUMO
uses traditional traffic signals, while AORTA adopts a much more general
\textit{reservation} system. A reservation tells a car when it is safe to take
its desired path through the intersection. Reservations can be allotted to
vehicles through more traditional means such as traffic signals or stop-sign
based intersection precedence, or through more efficient methods designed
specifically for autonomous vehicles \cite{JAIR08-dresner}. Based on experience
with SUMO, AORTA also displays more robust handling of data exported directly
from OSM. \commentpk{I am worried about the last line. It might be true, but it
is a fairly strong claim - we should put a citation of us handling something
that has been documented as not being handled via SUMO}

On the other hand, there are a number of simulators that specifically target
autonomous traffic systems. One such system is AIM \cite{JAIR08-dresner}, which
aims to optimize traffic flow of autonomous vehicles at a given intersection.
AIM studies problems at the scale of roughly a dozen intersections arranged in
a regular grid, while AORTA has the potential to apply some of the same
research at a city-wide scale to real-world road networks.

@@

The authors would like to thank Dr. Michael Quinlan for his support during the
seminal stages of AORTA and all OpenStreetMap contributers for providing free
maps.

>>>>

Computational processing power has made excellent advancements in the last two
decades. Parallel computing and the use of GPUs have enabled microscopic models
of traffic simulation to generate results at a meaningful scale (city-wide or
greater) \cite{nagel1994microscopic,shen2011agent}. As a result, a number of
multi-agent micro-simulators have been introduced in the past decade. We review
relevant simulators and other related work in this section.

OSM data has been used by traffic simulators in the past. MATSim is one such
multiagent simulator that focuses on performing large-scale simulations in a
relatively small amount of time \cite{balmer2009matsim}. Traffic demand is
supplied to MATSim in the form of \textit{plans} that an individual may intend
to follow in a given day. MATSim aims to iteratively improve these plans though
offline computation to maximize traffic throughput. In other words, it helps
individuals understand the best way to go about their daily routine to minimize
time spent in transit. This goal is somewhat different from that of AORTA,
where the demand supplied by individuals is taken as is. Rather than simply
improving routes, AORTA allows creating entirely different behaviors for both
vehicles and intersections.

Another popular open source traffic simulator that can use OSM data is SUMO
\cite{SUMO2011}, which shares the similar goals as AORTA. SUMO has been used to
study the effect of automated transportation systems, route planning of
individual vehicles, as well as dynamically adapting traffic signal policies to
increase traffic efficiency.  AORTA and SUMO differ in the manner in which
intersections are handled. SUMO uses traditional traffic signals, while AORTA
adopts a much more general \textit{reservation} system. A reservation tells a
car when it is safe to take its desired path through the intersection.
Reservations can be allotted to vehicles through more traditional means such as
traffic signals or stop-sign based intersection precedence, or through more
efficient methods designed specifically for autonomous vehicles
\cite{JAIR08-dresner}.

Efforts have been made to optimize traffic flow in the context of autonomous
vehicles. AIM \cite{JAIR08-dresner} is one such approach that aims to optimize
traffic flow of autonomous vehicles at a given intersection. The AIM approach
has been applied to a regular grid of four intersections
\cite{IROS11-hausknecht}, while AORTA has the potential to apply some of the
same research at a city-wide scale to real-world road networks.

@@

This work has taken place in the Learning Agents Research Group (LARG) at the
Artificial Intelligence Laboratory, The University of Texas at Austin. LARG
research is supported in part by grants from the National Science Foundation
(IIS-0917122), ONR (N00014-09-1-0658), and the Federal Highway Administration
(DTFH61-07-H-00030).

The authors would like to thank Dr. Michael Quinlan for his support during the
seminal stages of AORTA and all OpenStreetMap contributers for collecting the
map data used in this work. Efforts by the Freshman Research Initiative,
College of Natural Sciences, UT Austin have allowed for the development of this
research.
